---
title: "Lab 07 - Modelling course evaluations"
author: [TEAM NAME]
output: 
  tufte::tufte_html:
    css: ../lab.css
    tufte_variant: "envisioned"
    highlight: pygments
link-citations: yes

---

### Load packages 

```{r load-packages, message=FALSE, warning=FALSE}
library(tidyverse)
library(tidymodels)
library(patchwork)
```

### Read in data

```{r read-data}
evals<-read.csv("data/evals.csv", row.names=1)
```


### Exercise 1

```{r viz-score}
ggplot(evals, mapping = aes(x = score)) +
  geom_bar()
```

*The graph is skewed to the right, meaning that the most courses were given a score between 4 and 5. From this graph we can also tell that the most common score for a course to be given is 4.4, closely followed by 4.5.*

### Exercise 2

```{r viz-score-bty}
# add the code for each plot and assign them to the names as outlined below
# remove eval = FALSE from the code chunk options
# knit the document, and you'll see them appear next to each other
# this uses the patchwork package loaded above
# learn more about patchwork at https://patchwork.data-imaginist.com/
# it might be useful for your presentations!
plot_geom_point  <- ggplot(evals, aes(x = score,
                                      y = bty_avg)) +
                      geom_point()+
                      labs(title = "Score to Beauty Average",
                           subtitle = "Without Jitter")

plot_geom_jitter <- ggplot(evals, aes(x = score,
                                       y = bty_avg))+
                            geom_point(position = "jitter")+
                            labs(title = "Score to Beauty Average",
                                  subtitle = "With Jitter")

plot_geom_point + plot_geom_jitter
```

*Add your narrative here.*

### Exercise 3

```{r fit-score_bty_fit}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_bty_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(score ~ bty_avg, data = evals)
score_bty_fit
```

```{r tidy-score_bty_fit}
# remove eval = FALSE from the code chunk options after filling in the blanks
tidy(score_bty_fit)
```

*Add your linear model here. Don't worry too much about notation, you can use things like score-hat.*

### Exercise 4

```{r viz-score_bty_fit}
ggplot(evals, aes(x = score,
                  y = bty_avg))+
  geom_point(position = "jitter")+
  labs(title = "Score to Beauty Average",
       subtitle = "With Jitter")+
  geom_smooth(method = "lm",
              se = FALSE,
              fullrange = TRUE,
              aes(colour = "orange"))
```

### Exercise 5

*Add interpretation of intercept here.*

### Exercise 6

*Add interpretation of intercept here.*

### Exercise 7

```{r glance-score_bty_fit}
# remove eval = FALSE from the code chunk options after filling in the blanks
glance(score_bty_fit)
```

*Add interpretation of R-squared here.*

### Exercise 8

```{r viz-score_bty_fit-diagnostic, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_bty_aug <- augment(score_bty_fit$fit)

ggplot(___)
```

*Add your narrative here.*

### Exercise 9

```{r fit-score_rank_fit}
# fit model

# tidy model output
```

*Add your narrative here.*

### Exercise 10

```{r fit-score_gender_fit}
# fit model

# tidy model output
```

```{r score_gender_intercept, echo = FALSE, eval = FALSE}
# remove eval = FALSE from the code chunk options
score_gender_intercept <- tidy(score_gender_fit) %>% 
  filter(term == "(Intercept)") %>%
  select(estimate) %>%
  pull()
```

```{r score_gender_slope, echo = FALSE, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_gender_slope <- tidy(score_gender_fit) %>% 
  filter(term == "___") %>%
  select(___) %>%
  pull()
```

*Add your narrative here.*

### Exercise 11

```{r fit-score_bty_gender_fit}
# fit model

# tidy model output
```

*Add your narrative here.*

### Exercise 12

```{r glance-score_bty_gender_fit}
# glance model output
```

*Add your narrative here.*

### Exercise 13

*Add your linear model here. Don't worry about math notation, you can use things like score-hat.*

### Exercise 14

*Add your narrative here. One sentence is sufficient.*

### Exercise 15

*Add your narrative here. One sentence is sufficient.*

### Exercise 16

*Add your narrative here. One sentence is sufficient.*

### Exercise 17

*Add your narrative here. One sentence is sufficient.*

### Exercise 18

```{r fit-score_bty_gender_rank_fit}
# fit model

# glance model output
```

*Add your narrative here. One sentence is sufficient.*
